### 2013-12-11 Publications/2013-ISBI14/02-introduction.tex
Fixed some typos. Fixed vera font

Among all the difficulties that such a complex workflow raises, % \cite{jones_twenty-five_2010},
  we will address here the susceptibility-derived artifacts,
  for which \Gls*{epi} schemes are especially sensitive.
Magnetic susceptibility disturbs the magnetic field close to tissue interfaces.
This inhomogeneity of the field translates into a highly distorted anatomy
  and a significant signal destruction in certain regions of the brain 
  (e.g. the orbitofrontal lobe, for the proximity of the air surrounding sinuses).
This artifact has been well described, generally within the context of functional MRI,
  which also uses \gls*{epi}.

>>>>

Among all the difficulties that such a complex workflow raises \cite{jones_twenty-five_2010},
  we will address here the susceptibility-derived artifacts,
  for which \Gls*{epi} schemes are especially sensitive.
Magnetic susceptibility disturbs the magnetic field close to tissue interfaces.
This inhomogeneity of the field translates into a highly distorted anatomy
  and a significant signal destruction in certain regions of the brain 
  (e.g. the orbitofrontal lobe, for the proximity of the air surrounding sinuses).
This artifact has been well described, generally within the context of functional MRI,
  which also uses \gls*{epi}.
